---
title: "eBird/ML audio uploaders in India"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}

library(tidyverse)
library(lubridate)
library(magrittr)
library(patchwork)
theme_set(theme_bw())


media_csv_names <- list.files(pattern = "*.csv",
                              full.names = T)

eBird.users <- read.delim("ebd_users_relDec-2021.txt", 
                          sep = "\t", header = T, quote = "", 
                          stringsAsFactors = F, na.strings = c(""," ",NA))
names(eBird.users) <- c("OBSERVER.ID","FIRST.NAME","LAST.NAME")
eBird.users <- eBird.users %>% transmute(OBSERVER.ID = OBSERVER.ID,
                                         FULL.NAME = paste(FIRST.NAME, LAST.NAME))

data0 <- media_csv_names %>% 
  lapply(read_csv) %>% 
  bind_rows() %>% 
  rename(SAMPLING.EVENT.IDENTIFIER = `eBird Checklist ID`,
         FULL.NAME = Recordist) %>%
  rename_with(~ toupper(.)) %>% 
  rename_with(~ gsub(" ", ".", .x)) %>% 
  left_join(eBird.users)

data1 <- data0 %>% 
  group_by(FULL.NAME) %>% 
  summarise(TOT.AUDIO = n(),
            SP.AUDIO = n_distinct(COMMON.NAME)) %>% 
  arrange(desc(TOT.AUDIO), desc(SP.AUDIO))

data2 <- data1 %>% 
  filter(TOT.AUDIO >= 500, SP.AUDIO >= 200)

data3 <- data1 %>% 
  filter(TOT.AUDIO >= 200, SP.AUDIO >= 100)

```

# Recordist histogram

How recordists are distributed across numbers of total audio and species audio files uploaded:

(Y axis has been cut off to highlight our interest; blue is lenient, red is stringent)

```{r, echo=FALSE}

(ggplot(data1) +
   geom_histogram(aes(TOT.AUDIO), binwidth = 100) +
   coord_cartesian(ylim = c(0,25)) +
   geom_vline(xintercept = 200, col = "skyblue") +
   geom_vline(xintercept = 500, col = "darkred")) /
  (ggplot(data1) +
     geom_histogram(aes(SP.AUDIO), binwidth = 10) +
     coord_cartesian(ylim = c(0,25)) +
     geom_vline(xintercept = 100, col = "skyblue") +
     geom_vline(xintercept = 200, col = "darkred"))

```

# Candidates

On filtering using the two basic thresholds discussed, the following lists of candidates were obtained.

**500 total, 200 species:** `r n_distinct(data2$FULL.NAME)` candidates

```{r, echo=FALSE}
knitr::kable(data2)
```

**200 total, 100 species:** `r n_distinct(data3$FULL.NAME)` candidates

```{r, echo=FALSE}
knitr::kable(data3)
```